Inter-task effects lead to an unexpected bias in human computation

### 2014-08-01 docs/publications/2014.05_PNAS/manuscript.tex
embed figures in manuscript, merge orientation and specificity figs

%        File: pnas1.tex
%     Created: Wed Apr 30 04:00 pm 2014 E
% Last Change: Wed Apr 30 04:00 pm 2014 E
%
\documentclass[a4paper]{report}
\usepackage[hmargin=1in,vmargin=1in]{geometry}

@@

\subsection*{Experimental Setup}
We solicited 900 AMT workers to perform an image-labeling task relating to
food and culture.  The workers were randomly assigned to one of seven 
treatments shown in \textbf{Table 1}.  Workers were first shown brief 
instructions.  Depending on their treatment, workers were then shown the 
name of a research funder, or this step was skipped.  When shown, 
the funder name was either
``The Global Foundation for Cultural Recognition'', or 
``The National Foundation for Nutritional Awareness''.  Next, workers were
shown ten images, one at a time, and were required to label each image with
five descriptive labels.  For the purpose of analysis, we divide the images
into the \textit{initial} and \textit{final} sets, which are respectively the 
first five and last five images shown.  However, from the perspective of the 
worker, there was no 
distinction or interruption between the initial and final sets. 
The initial set was chosen from one of three sets, depending on the 
treatment, while the final set was always the same.

@@

@@

\paragraph{Earlier tasks orient focus during later tasks.} Having 
demonstrated both inter-task and framing effects, we next
investigated the \textit{nature} of these effects.  To this
end, we constructed an ontology of all the labels attributed to
the final images.   
The ontology is a directed acyclic graph of terms,
with directed edges drawn from abstractions toward instances.  For example,
our ontology contains the path \texttt{food} $\to$ \texttt{ingredients} $\to$ 
\texttt{vegetables} 
$\to$ \texttt{tomato}. We provide more detail about the construction of the 
ontology in the \textbf{Materials and Methods} section.

@@

\paragraph{Earlier tasks affect attention to detail during later tasks.} 
Using the ontology described
in the previous section, we compared treatments in their degree of specificity.
When comparing two labels $\ell_1$ and $\ell_2$ produced by different workers,
we say that $\ell_2$ is more specific than $\ell_1$ if there is a 
\textit{directed path} from $\ell_1$ to $\ell_2$.  If there is no directed path
between $\ell_1$ and $\ell_2$, then they are non-comparable.  As an example,
\texttt{tomato} is more specific than \texttt{food}, while \texttt{statue}
and \texttt{food} are non-comparable.

@@

>>>>

%        File: pnas1.tex
%     Created: Wed Apr 30 04:00 pm 2014 E
% Last Change: Wed Apr 30 04:00 pm 2014 E
%
\documentclass[a4paper]{report}
\usepackage[hmargin=2cm,vmargin=2cm]{geometry}

@@

\subsection*{Experimental Setup}
\begin{table}[t]
\centering
	\begin{tabular}{ l  l  l }
		\hline                       
		Treatment & Funder & Priming Image Set	\\ 
		\hline                       
		$\textsc{ambg}$ & None & Ambiguous\\
		$\textsc{cult}_{img}$ & None & Cultural\\
		$\textsc{cult}_{fund}$ & Cultural & Cultural\\
		$\textsc{cult}_{fund,img}$ & Cultural & Cultural\\
		$\textsc{ingr}_{img}$ & None & Ingredients\\
		$\textsc{ingr}_{fund}$ & Nutritional & Ingredients\\
		$\textsc{ingr}_{fund, img}$ & Nutritional & Ingredients\\
		\hline  
	\end{tabular}

%\begin{addmargin}[11em]{11em}
%	\vspace{2mm}
%	$^a$\footnotesize{The full funder names used were ``The Glodal Foundation
%		for Cultural Recognition'' and ``The National Foundation for 
%		Nutritional Awareness''.}
%\end{addmargin}

	\caption{Workers were uniformly randomly
		assigned to one of the treatments listed above.}
	\label{table:1}
\end{table}

\begin{figure}
	\includegraphics[scale=1.00]{figs/taskImages/testImages.jpg}
	\caption{Testing image set. These images were presented to all workers in 
		the order shown after the priming set of images.}
\end{figure}

\begin{figure}
	\includegraphics[scale=1.00]{figs/taskImages/ambiguous.jpg}
	\caption{ Ambiguous image set. These images were presented to workers from 
		certain treatements (see \textbf{Table 1}) in the order shown.}
\end{figure}

\begin{figure}
	\includegraphics[scale=1.00]{figs/taskImages/cultural.jpg}
	\caption{Cultural image set. These images were presented to workers from 
		certain treatements (see \textbf{Table 1}) in the order shown.}
\end{figure}

\begin{figure}
	\includegraphics[scale=1.00]{figs/taskImages/ingredients.jpg}
	\caption{ Ingredients image set. These images were presented to workers 
		from certain treatements (see \textbf{Table 1}) in the order shown.}
\end{figure}

We solicited 900 AMT workers to perform an image-labeling task relating to
food and culture.  The workers were randomly assigned to one of seven 
treatments shown in \textbf{Table 1}.  Workers were first shown brief 
instructions.  Depending on their treatment, workers were then shown the 
name of a research funder, or this step was skipped.  When shown, 
the funder name was either
``The Global Foundation for Cultural Recognition'', or 
``The National Foundation for Nutritional Awareness''.  Next, workers were
shown ten images, one at a time, and were required to label each image with
five descriptive labels.  For the purpose of analysis, we divide the images
into the \textit{initial} and \textit{final} sets, which are respectively the 
first five and last five images shown.  However, from the perspective of the 
worker, there was no 
distinction or interruption between the initial and final sets. 
The initial set was chosen from one of three sets, depending on the 
treatment, while the final set was always the same.

@@

\begin{figure}
	\includegraphics[scale=0.94]{figs/f1-thetas_full_pairwise25_img1.pdf}
	\caption{ $F_1$ score and $\theta_\text{NB}$ for the various 
priming treatments, as measured using a Naive Bayes classifier. Each panel 
presents classifier performance results that indicate the difference in
priming between a basis 
treatment, indicated in the inset, and the other treatments, indicated on the
abscissa. }
\end{figure}

@@

\paragraph{Earlier tasks orient focus during later tasks.} 
\begin{figure}
	\includegraphics[scale=0.94]{figs/orientation_specificity.pdf}
	\caption{Percent label composition (culture- vs food-oriented labels) for 
		various images and treatments.  Panel A shows the composition of 
		labels, aggregated over all treatments, as a function of test image.
		Panel B shows the composition of labels, aggregated over all images, as
		a function of treatment.  Panel C shows the composition of labels 
		attributed to the first test image by various treatments.}
\end{figure}

Having demonstrated both inter-task and framing effects, we next
investigated the \textit{nature} of these effects.  To this
end, we constructed an ontology of all the labels attributed to
the final images.   
The ontology is a directed acyclic graph of terms,
with directed edges drawn from abstractions toward instances.  For example,
our ontology contains the path \texttt{food} $\to$ \texttt{ingredients} $\to$ 
\texttt{vegetables} 
$\to$ \texttt{tomato}. We provide more detail about the construction of the 
ontology in the \textbf{Materials and Methods} section.

@@

\paragraph{Earlier tasks affect attention to detail during later tasks.}

Using the ontology described
in the previous section, we compared treatments in their degree of specificity.
When comparing two labels $\ell_1$ and $\ell_2$ produced by different workers,
we say that $\ell_2$ is more specific than $\ell_1$ if there is a 
\textit{directed path} from $\ell_1$ to $\ell_2$.  If there is no directed path
between $\ell_1$ and $\ell_2$, then they are non-comparable.  As an example,
\texttt{tomato} is more specific than \texttt{food}, while \texttt{statue}
and \texttt{food} are non-comparable.

@@

\begin{figure}
	\includegraphics{figs/longitudinal_theta_excess-culture.pdf}
	\caption{Excess culture-oriented label composition in the labels provided
		by $\textsc{cult}_{img}$ as compared to $\textsc{ambg}$, for various
		test images (see \textbf{Eq. 1} for calculation).
	}
\end{figure}
